Describing the C-space of asynchronous periodic task using DIT

### 2013-07-26 dit-paper_ieee.tex
i dunno

The first periodic DIT, if it exists, must occur in the transitive period. Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transitive period at instant $t_d - k H$ (a contradiction).\\

We show (???) that we can restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the first periodic DIT exists. This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.\\

@@

Such a linear problem can be solved by the simplex algorithm. However, here the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within. The naive method would be to directly test each constraints of the set against all the others, we present a similar method with an efficient preprocessing in Algorithm \ref{alg:prunRedun}.\\

@@

\subsection{Numerical Example}

@@

We now apply algorithm \ref{alg:prunRedun} to remove redundancies, leaving us with the following constraints:
$$
\left\{
	\begin{array}{ccccc}
		& & C_2 & \leqslant & 2 \\
		C_1 & + & C_2 & \leqslant & 7
	\end{array}
\right.
$$
The C-space thus contains 11 points $(C_1, C_2) = (1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(6, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$, $(4, 2)$ and $(5, 2)$.\\

@@

\section{Example}

>>>>

The FPDIT, if it exists, must occur in the transitive period. Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transitive period at instant $t_d - k H$ (a contradiction).\\

As the FPDIT happened when all tasks were in the system, we know that the system will arrive in the exact same state one hyperperiod later ($t_d + H$)
We show (???) that we can restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the first periodic DIT exists. This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.\\

@@

Such a linear problem can be solved by the simplex algorithm. However, in our case the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within. A naive method would be to test each constraint against all the others. We present a similar method with an efficient preprocessing when most constraints are redundant in Algorithm \ref{alg:prunRedun}.\\

@@

\section{Numerical Example}

@@

We now apply Algorithm \ref{alg:prunRedun} to remove redundancies, leaving us with the following constraints:
$$
\left\{
	\begin{array}{ccccc}
		& & C_2 & \leqslant & 2 \\
		C_1 & + & C_2 & \leqslant & 7
	\end{array}
\right.
$$
The C-space thus contains 11 points $(C_1, C_2) = (1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(6, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$, $(4, 2)$ and $(5, 2)$.\\

@@
